Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2021-11-14 doc/JFLA2022/paper.tex

\begin{abstract}
  \Hydras is a collaborative library of discrete mathematics for the
  \coq proof assistant, developed as part of the \community organization
  on GitHub. The Coq code is accompanied
  by an electronic book, generated with the help of the \alectr
  literate proving tool. We present the evolution of the mathematical
  contents of the library since former presentations at JFLA meetings.
  Then, we describe how the structure of the project is determined
  by two requirements which must be continuously satisfied.
  First, the Coq code needs to be compatible with its ever-evolving
  dependencies (the Coq proof assistant and several Coq packages both from
  inside and outside \community) and reverse dependencies (\community
  projects that depend on it). Second, the book needs to be consistent
  with the Coq code, which undergoes frequent changes to improve
  structure and include new material. We believe \Hydras demonstrates
  that books on formalized mathematics are not limited to
  providing exposition of theories and reasoning techniques---they
  can also provide inspiration and entertainment that transcends educational goals.
\end{abstract}

>>>>

\begin{abstract}
  \Hydras is a collaborative library of discrete mathematics for the
  \coq proof assistant, developed as part of the \community organization
  on GitHub. The Coq code is accompanied
  by an electronic book, generated with the help of the \alectr
  literate proving tool. We present the evolution of the mathematical
  contents of the library since former presentations at JFLA meetings.
  Then, we describe how the structure of the project is determined
  by two requirements which must be continuously satisfied.
  First, the Coq code needs to be compatible with its ever-evolving
  dependencies (the Coq proof assistant and several Coq packages both from
  inside and outside \community) and reverse dependencies (\community
  projects that depend on it). Second, the book needs to be consistent
  with the Coq code, which undergoes frequent changes to improve
  structure and include new material. We believe \Hydras demonstrates
  that books on formalized mathematics are not limited to
  providing exposition of theories and reasoning techniques---they
  can also provide inspiration and entertainment that transcend educational goals.
\end{abstract}
